\begin{enumerate}
    \item All Executive and Non-Executive positions will be elected positions.
    \item Executive positions may only be held by youth members who have been registered with the Company/Crew for a period of at least one year.\footnote{An exception to this can be made based on the current group registration.}
    \item There should be at least one member from the Venturer section and one from the Rover section on the Executive.\footnotemark[\value{footnote}]
    \item Executive positions within the Company/Crew are President, Vice President, Treasurer, Secretary, Quartermaster, and Contact Advisor.
    \item Non-Executive positions within the Company/Crew shall include Master at Arms and Advisor.
    \item Executive and Non-Executive position terms begin and end with the scouting year.
    \item Annual elections for executive positions are to be held during the month, 3 months prior to the end of the scouting year.
\end{enumerate}

\subsection{Duties of the President}\label{subsec:duties-of-the-president}
\begin{enumerate}
    \item Organize Executive and Company/Crew meetings, ensure all members are notified working in conjunction with the Secretary.
    \item Provide leadership to the Company/Crew at meetings and activities.
    \item Chair Executive and Company/Crew meetings.
    \item Ensure all members and Advisors are kept informed.
    \item Attend monthly Group Committee meetings, representing the Company/Crew including making presentations, and other related tasks.
\end{enumerate}

\subsection{Duties of the Vice-President}\label{subsec:duties-of-the-vice-president}
\begin{enumerate}
    \item Act in place of the President when required.
    \item Provide leadership to the Company/Crew at meetings and events.
    \item Keep absentee members informed of current and upcoming activities.
    \item Execute such tasks as assigned by the President.
    \item Ensure adherence to the Constitution and Code of Conduct.
\end{enumerate}

\subsection{Duties of the Secretary}\label{subsec:duties-of-the-secretary}
\begin{enumerate}
    \item Organize Executive and Company/Crew meetings, and ensure all members are notified, working in conjunction with the President.
    \item Maintain a record of attendance and notices of absence for all meetings.
    \item Record proper minutes of Executive and Company/Crew meetings.
    Provide minutes to all members of the meeting.
    \item Report on all internal communication by the Company/Crew.
    \item Keep up-to-date membership list with phone numbers and e-mail addresses.
    \item Keep copies of the minutes from Group Committee meetings.
    \item Keep copies of the Company/Crew Constitution.
\end{enumerate}

\subsection{Duties of the Treasurer}\label{subsec:duties-of-the-treasurer}
\begin{enumerate}
    \item Maintain up-to-date records of the Company/Crew financial state, supported by documented accounts or revenues and expenses.
    \item Report financial activity and status monthly to the Company/Crew.
    \item Submit Company/Crew financial records for Advisor(s) and Executive for review quarterly.
    \item Submit Company/Crew financial records to Group Committee for auditing annually in September.
\end{enumerate}

\subsection{Duties of the Quartermaster}\label{subsec:duties-of-the-quartermaster}
\begin{enumerate}
    \item Maintain a record of all equipment belonging to the Company/Crew.
    \item Ensure the storage and maintenance of equipment belonging to the Company/Crew.
    \item Provide a list of equipment to members planning events for sign-out and use at said events.
    \item Ensure all equipment is necessary and in good repair.
\end{enumerate}

\subsection{Duties of the Master at Arms}\label{subsec:duties-of-the-master-at-arms}
\begin{enumerate}
    \item Ensure adherence to Robert's Rules of Order.
\end{enumerate}

\subsection{Duties of the Advisors}\label{subsec:duties-of-the-advisors}
\begin{enumerate}
    \item To assist the Company/Crew to achieve their objectives, whether group or individual.
    \item Advisors suggest and advise, but do not order, excepting that Advisors have veto powers on issues of safety, or any rules/laws/by-laws that come into play.
    \item Special meetings may be held without Advisors present after notification (with complete details) has been provided to the Advisors.
    \item Advisors may permit activities without Advisors presence, after approval of details and after the competence of those attending has been demonstrated.
    \item The contact Advisor is ultimately responsible to the sponsoring Group Committee for the actions of the Company/Crew.
\end{enumerate}
A motion of abandonment of position may be raised after any Executive has missed three consecutive meetings without a valid reason or has failed to carry out their duties without a valid reason.
If for any reason the members of the Company/Crew wish to add or remove an Advisor, all changes in the Advisor team must first be approved by the Group Commissioner of the Voyageur Council Service Alliance.