\documentclass{Service_Corps_Document}
\stdSetup
\begin{document}
    \def \Title {Constitution}
    \def \Company {Service Corps}
    \def \versionNumber {4.3}
    \stdFooter
    \begin{titlepage}
        \stdTitlePage
    \end{titlepage}

    \tableofcontents

    \newpage


    \section{NAME \& ESTABLISHMENT}\label{sec:name-&-establishment}
    \begin{enumerate}
        \item The name of the Company/Crew shall be "Service Corps" established under the Charter of Scouts Canada dated September 2011.
        The sponsorship of the Company/Crew shall be the Royal Canadian Legion Branch 480.
        \item The Company/Crew is part of and subscribes to the BY-LAW, POLICIES, AND PROCEDURES of Scouts Canada (BP\&P).
        \item The members of the Company/Crew will endeavour to live according to the Mission, Principles, Practices, and Promise of Scouts Canada.
        The members of the Company/Crew will endeavour to plan activities (service-oriented, program or social) which will enable all members to participate actively.
    \end{enumerate}


    \section{MEMBERSHIP}\label{sec:membership}
    \input{constitution_membership}


    \section{EXECUTIVE}\label{sec:executive}
    \input{constitution_executive}


    \section{PROGRAM}\label{sec:program}
    \begin{enumerate}
        \item The central program theme of the Company/Crew shall be Community Service.
        The Company/Crew may also take part in Social Activities and camping.
        The majority of Company/Crew program planning, training, and resources will be directed toward these activities.
        \item The Company/Crew at large will determine by vote, other program activities and objectives for action by the Executive.
        \item The Company/Crew at large will determine the classification of all events, i.e., mandatory, major, elective, or fundraising.
        \item All motions must be put forward to the Group.
        They must be seconded by another member and require a vote of 50\% plus one.
        No vote can be accepted without quorum.
        Quorum is 50\% of voting members plus one.
    \end{enumerate}


    \section{UNIFORMS \& INSIGNIA}\label{sec:uniforms-&-insignia}
    All members must wear a uniform to all meetings, events, or activities where it enhances the image of the Company/Crew, e.g., formal events, community service, or fundraising.
    The sponsor of activities may dictate some uniform requirements.
    All members must treat their uniform with care.

    \subsection{Scouts Canada Uniform}\label{subsec:scouts-canada-uniform}
    \begin{enumerate}
        \item Full Dress Uniform - Scouts Canada uniform shirt with appropriate crests, red/black Service Corps necker, tan pants and black or brown shoes
        \item Full Uniform - Scouts Canada uniform shirt with appropriate crests and red/black Service Corps necker
        \item Activity Uniform - Scouts Canada t-shirt or Golf shirt and red/black Service Corps necker or group apparel.
        \item Event Wear - May consist of, but is not limited to, Scouts activity wear, special items provided from event organizers or specialized unit wear such as scarves, toques, neckers, and vests.
    \end{enumerate}


    \section{AMENDMENTS}\label{sec:amendments}
    Should the need arise to amend the Constitution or Code of Conduct, the following steps should be followed.
    \begin{enumerate}
        \item All members must be informed seven days before a motion to amend the Constitution or Code of Conduct is put forward.
        \item The potential amendments must be approved by Group Commissioner of the Voyageur Council Service Alliance
        \item A motion containing the potential amendments is to be put forward at a group meeting.
        \item If passed, a written page of the amendment is to be produced and attached to the Constitution or Code of Conduct until said time that it can be updated.
        \item All amendments must be added to the Constitution or Code of Conduct before the Executive's term ends.
    \end{enumerate}


    \section{DISSOLUTION}\label{sec:dissolution}
    Should the Company/Crew at any time dissolve or cease to exist:
    \begin{enumerate}
        \item All monies and assets purchased and still held at the date of dissolution or cessation of existence shall revert to the Voyageur Council Service Alliance.
        \item Upon payment of any outstanding debts, all remaining funds and assets shall revert to the Voyageur Council Service Alliance, to be held for a period of no less than two years as a contingency for the re-establishment of a new Company/Crew and then distributed for the benefit of the youth of said Group.
        \item All records of the Company/Crew shall be placed under the jurisdiction of the Voyageur Council Service Alliance, in possession of the Group Administrator to be held for a period of no less than two years as a contingency for the re-establishment of the Company/Crew.
    \end{enumerate}
\end{document}